Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2017-11-03 paper/galsize_paper.tex
Minor cleanup to methods section

In the first class of models we explore, we suppose that stellar mass $\mstar$ is the statistical regulator of $\rhalf,$ so that galaxy sizes are drawn from a log-normal distribution centered at $\median{\rhalf}{\mstar}.$ To implement this model, for simplicity we directly tabulate $\median{\rhalf}{\mstar}$ directly from the data, rather than pursue a parametric form \citep[see, e.g.,][]{zhang_yang17}.

@@

As we will show in \S\ref{sec:results}, the chief ingredient needed to recover the observed clustering properties of galaxies is that satellites need to be smaller than centrals of comparable halo mass. Thus it is natural to consider a class of models in which stellar mass is stripped from satellite galaxies after infall.
 %satellites lose stellar mass in a way that mimics what is seen in high-resolution hydrodynamical simulations.

>>>>

In the first class of models we explore, we suppose that stellar mass $\mstar$ is the statistical regulator of $\rhalf,$ so that galaxy sizes are drawn from a log-normal distribution with $0.2$ dex of scatter centered at $\median{\rhalf}{\mstar}.$ To implement this model, for simplicity we directly tabulate $\median{\rhalf}{\mstar}$ directly from the data, rather than pursue a parametric form \citep[see, e.g.,][]{zhang_yang17}.

@@

As we will show in \S\ref{sec:results}, the chief ingredient needed to recover the observed clustering properties of galaxies is that satellites need to be smaller than centrals of comparable halo mass. Thus it is natural to consider a class of models in which stellar mass is stripped from satellite galaxies after infall.
